\Large {\bf Flow-guided Analysis of System-level Post-silicon Traces Under Limited Observability}

### 2015-09-07 paper.tex
Added some stuff to intro
added a sentence to intro
fixing some git issues

@@

A central component of post-silicon validation is to
correlate trace from silicon execution with the intended
behavior of the sysem.  As an example, consider a silicon
execution of a smartphone executing a post-silicon use case
where the end-user browses the Web while listening to music
and sending and receiving occasional text messages.  Such a
an execution trace would involve activities from the CPU,
audio controller, display controller, wireless radio
antenna, etc., reflecting the interleaved execution of
several communication protocols.  On the other hand, due to
observability limitations, only a small small number of
participating signals can be actually traced during silicon
execution.  Furthermore, due to electrical perturbations,
silicon data can be noisy, lossy, and ambiguous.
Consequently, it is non-trivial to identify all
participating protocols and pinpoint the ``right''
interleaving that results in an observed trace.

In this paper, we consider the problem of reconstructing
protocol-level behavior from silicon traces in SoC designs.

>>>>

\newcommand{\eg}{\mbox{{\em e.g.}}}

@@

A central component of post-silicon validation of SoC
designs is to correlate trace from silicon execution with
the intended system-level transactions.  An SoC design is
typically composed of a large number of pre-designed
hardware or software blocks (often referred to as
``intellectual properties'' or ``IPs'') that coordinate
through complex protocols to implement system-level
behavior.  Any execution trace of the system involves a
large number of interleaved instances of these protocols.
For example, consider a smartphone executing a usage
scenerio where the end-user browses the Web while listening
to music and sending and receiving occasional text messages.
Typical post-silicon validation use-case involve exercising
such scenarios.  An execution trace for this scenario would
involve activities from the CPU, audio controller, display
controller, wireless radio antenna, etc., reflecting the
interleaved execution of several communication protocols.
On the other hand, due to observability limitations, only a
small small number of participating signals can be actually
traced during silicon execution.  Furthermore, due to
electrical perturbations, silicon data can be noisy, lossy,
and ambiguous.  Consequently, it is non-trivial to identify
all participating protocols and pinpoint the ``right''
interleaving that results in an observed trace.

In this paper, we consider the problem of reconstructing
protocol-level behavior from silicon traces in SoC designs.
More specifically, given a collection of system-level
communication protocols and a trace of (partially observed)
hardware signals, our approach infers, with a certain
measure of confidence, the protocol instances (and their
interleavings) being exercised by the trace.  We show how to use symbolic simulation and
